Shaping the Perception of a Robot by Cognitive Priming

### 2016-08-30 main.tex
Some old proof-reading

These two questions translate into several experimental hypotheses, whose design
was guided by the following intuition: \emph{the more we ascribe cognitive
capabilities to an agent, the more likely we are to focus on its head (\ie the
brain) when
interacting with it}, which suggests an eye-tracking-based investigation.

@@

Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
stimuli that induce \emph{shallow} or \emph{higher} expectations regarding the
cognitive skills of the robot. This hypothesis is to be tested by asking
participants to rate the interactions depicted by the stimuli as being more
\emph{machine-like} (low ascription of cognitive skills) or \emph{human-like}
(higher expectation of cognitive competency).

@@

Third, we hypothesise that in the \emph{human-like} condition (higher ascription
of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (low ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

@@

\subsection{Discussion of the Results}

The presented results bring some light on our initial hypotheses.

The significant correlation between deep \vs shallow conditions and the
answers to the question \emph{Were the task more robot-like or human-like?}
shows that our manipulation was successful, and that a shallow cognitive
context was indeed associated to a robot-like situation, while a deeper
cognitive priming was associated to a human-like situation (\h{1}). This is
already an interesting result: subtle changes in the cognitive priming are
recognised and clearly interpreted in terms of human-likeness.

>>>>

These two questions translate into several experimental hypotheses, whose design
was guided by the following high-level hypothesis: \emph{the more we ascribe cognitive
capabilities to an agent, the more likely we are to focus on its head (\ie the
brain) when interacting with it}. As such, this hypothesis naturally suggests an
eye-tracking-based investigation.

@@

Our baseline hypothesis \h{1} is that cognitive priming allows us to effectively create
stimuli that induce \emph{lower} or \emph{higher} attribution of human-likeness
to the robot. This hypothesis can be tested by asking
participants to rate the interactions depicted by the stimuli as being more
\emph{machine-like} or \emph{human-like}.

@@

Third, we hypothesise that in the \emph{human-like} condition (which we
interpret as well as a higher ascription of cognitive skills to the robot), the participants' gaze will be directed
significantly more towards the head of the robot than in the \emph{machine-like}
condition (interpreted as a lower ascription of cognitive skills) (\h{3}). If verified, it
effectively means that the expectations held by the participants regarding the
cognitive capabilities of the robot are reflected by the eye fixations on the
head of the robot.  The hypothesis can be tested by comparing gaze fixations in
the two conditions (\emph{human-like} \vs \emph{machine-like}).

@@

The significant impact of the deep \vs shallow commands implication on the
answers to the question \emph{Were the tasks more robot-like or human-like?}
shows that our manipulation was well recognized, and that a shallow cognitive
context was indeed perceived to elicit a ``robot-like'' situation, while a deeper
cognitive priming was perceived as a ``human-like'' situation. This supports our
ifirst hypothesis \h{1}: even indirect hints at the cognitive capabilities of a robot are
sufficient to elicit significantly increased attribution of human-likeness.
